---
title: "Corona Africa"
# author: "Cyrus Herder"
# date: "3/24/2020"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    theme: flatly
    orientation: rows
---


```{r setup, include=FALSE}
rm(list = ls())
suppressMessages({
library("flexdashboard")
library("shinydashboard")
library("ggplot2")
library("ggthemes")
library("shiny")
library("countrycode")
library("rvest")
library("xml2")
library("leaflet")
library("leafpop")
library("purrr")
library("tibble")
require("rgdal")
require("dplyr")
require("leaflet")
})
#setwd(normalizePath(dirname(rstudioapi::getActiveDocumentContext()$path)))
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
source("Cleaning.R")
```

Home {data-icon="fa-home"}
=====================================


Row
-----------------------------------------------------------------------


### Total {.value-box}

```{r}

flexdashboard::valueBox(value = paste(format(sum(Africa$Cnf, na.rm = T), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```

### Active {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(Africa$Active, na.rm = T), big.mark = ","), "", sep = " "),
         caption = "Active", icon = "fas fa-gratipay", 
         color = active_color)

```

### Recovered {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(Africa$Rec, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(Africa$Rec, na.rm = TRUE) / sum(Africa$Cnf), 1), 
                       "%)", sep = ""), 
         caption = "Recovered", icon = "fas fa-heartbeat", 
         color = recovered_color)

```

### Deaths {.value-box}

```{r}

flexdashboard::valueBox(value = paste(format(sum(Africa$Dth, na.rm = TRUE), 
                                             big.mark = ","), " (",
                       round(100 * sum(Africa$Dth, na.rm = TRUE) / sum(Africa$Cnf), 1), 
                       "%)", sep = ""),
         caption = "Deaths", icon = "fas fa-angellist", 
         color = death_color)
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------


### Africa Cases Distribution

```{r}
AFR <- as.data.frame(Africa %>% filter(AfricaCheck==1)) %>% arrange(desc(Active))

AFR$Country <- factor(AFR$Country, levels = unique(AFR$Country)[order(AFR$Active, decreasing = TRUE)])
```

```{r df_summary}
plotly::plot_ly(data = AFR, 
                x = ~ Country, 
                y = ~ Active, 
                type = "bar", 
                name = "Active",
                marker = list(color = active_color)) %>%
  plotly::add_trace(y = ~ Rec, 
                    name = "Recovered",
                    marker = list(color = recovered_color)) %>%
  plotly::add_trace(y = ~ Dth, 
                    name = "Died",
                    marker = list(color = death_color)) %>%
  plotly::layout(barmode = 'stack',
                 
                 yaxis = list(title = "Total Cases",
                              type = "log"),
                 xaxis = list(title = "",
                              range = as.character(sort(unique(as.numeric(AFR$Active)),decreasing = FALSE))),
                 hovermode = "compare", 
                 margin =  list(b = 10, 
                                t = 10, 
                                pad = 2
                 ))

```


### Global Smooth Trend 

```{r}
smoothtrend <- Main.df %>% #filter(AfricaCheck==1) %>% 
  mutate(Active = Confirmed - (Recovered+Deaths)) %>% 
  group_by(Dates,Country) %>% 
  summarise(Confirmed = max(Confirmed, na.rm = T),
            Active = max(Active, na.rm = T),
            Recovered = max(Recovered, na.rm = T),
            Deaths = max(Deaths, na.rm = T)) %>% 
  group_by(Dates) %>% 
  summarise(Confirmed = sum(Confirmed, na.rm = T),
            Active = sum(Active, na.rm = T),
            Recovered = sum(Recovered, na.rm = T),
            Deaths = sum(Deaths, na.rm = T)) %>% 
  
  tidyr::gather(Categories, TotalCases,Confirmed: Deaths)

cols<- c("purple","#1197fb","#ff6601","forestgreen")
hc <- hchart(smoothtrend, type = "line", hcaes(x = Dates, y = TotalCases, group = Categories)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Global Daily Trend", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Global Trends") %>% 
  hc_subtitle(text = paste(format(max(smoothtrend$TotalCases, na.rm = T),big.mark = ","),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_darkunica()) %>% 
  hc_colors(cols)

hc
```


Global Cases Summary {data-orientation=columns data-icon="fa-globe"}
=====================================


Column
-----------------------------------------------------------------------

### Total Cases

```{r}
  
Tt <- max(Totals$TotalCases, na.rm = T)

hc <- hchart(Totals, type = "column", hcaes(x = Year_Month, y = TotalCases)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Total Number of Cases") %>% 
  hc_subtitle(text = paste(Tt,"Cases", sep = " ")) %>% 
   hc_add_theme(hc_theme_monokai())

hc

```

Column
-----------------------------------------------------------------------

### Total Cases

```{r}
Tt2 <- max(Totals$TotalCases, na.rm = T)

hc <- hchart(Totals, type = "column", hcaes(x = Year_Month, y = TotalCases, group = Categories)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Time Comparison of Coronavirus") %>% 
  hc_subtitle(text = paste(Tt2,"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_monokai())

hc

```






```{r, eval=FALSE}
### Kenya Counties

# library(utils)
# message <- "This data is not upto date,its Very difficult to get Collated data from Kenyan Govt"
#winDialog(type = c("ok", "okcancel", "yesno", "yesnocancel"), message)

source("C:\\Users\\Cyrus Muriithi\\Documents\\GithubRepos\\Kenyan Counties.R")



ken_regions <- readOGR("C:\\Users\\Cyrus Muriithi\\Documents\\GithubRepos\\KEN_adm_shp","KEN_adm1", verbose = F, stringsAsFactors = FALSE)
ken_boundaries <- readOGR("C:\\Users\\Cyrus Muriithi\\Documents\\GithubRepos\\KEN_adm_shp","KEN_adm0", verbose = F, stringsAsFactors = FALSE)

Counties$NAME_1<- as.character(Counties$NAME_1)
ken_regions@data$NAME_1 <- as.character(ken_regions@data$NAME_1)
ken_regions@data <- left_join(ken_regions@data, Counties,by ="NAME_1")


county_map <- leaflet(ken_regions) %>%
  #setView(40.01, -1.835, zoom = 6) %>% 
  addProviderTiles(providers$OpenStreetMap)#,options = providerTileOptions(minZoom=6, maxZoom=8)) 

bins <- c(0,10,30,50,100,250)
pal <- colorBin("YlOrRd", domain = ken_regions@data$Cases, bins = bins)
confirmed_color <- "purple"
ppercent <- "#db1919"


labels <- sprintf(
  paste0("<strong>%s</strong><br/>",
    "Cases: ",
    purrr::map(glue::glue("<span style='color: {confirmed_color};'>
                          {ken_regions@data$Cases}</span>"),htmltools::HTML),
    "<br>",
    "Percent: ",
    purrr::map(glue::glue("<span style='color: {ppercent};'>
                          {ken_regions@data$Percent}</span>"),htmltools::HTML)
  ),
  ken_regions@data$NAME_1, ken_regions@data$Cases,ken_regions@data$Percent
) %>% lapply(htmltools::HTML)

county_map <- county_map %>% 
  addPolygons(data=ken_boundaries,
              weight = 2,opacity = 1,
              color = "white",dashArray = "3",
              fillOpacity = 0.7,
              highlight = highlightOptions(
                weight = 5,color = "#0000f7",
                dashArray = "",fillOpacity = 0.7,
                bringToFront = FALSE))%>%
  addPolygons(
    fillColor = ~pal(Cases),
    weight = 2,opacity = 1,
    color = "#007c00",dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 2.5,color = "#0000f7",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", 
                   padding = "3px 8px"),
      textsize = "15px",
      direction = "auto"))

county_map %>% addLegend(pal = pal, 
                         values = ~Cases, 
                         opacity = 0.5,
                         #title = "Number of Cases:<br>(Confirmed)",
                         title = glue::glue("{nrow(Counties)} Counties:<br>(Confirmed Cases: {paste('',format(sum(ken_regions@data$Cases, na.rm=T), big.mark = ','), sep =' ')})"),
                         position = "bottomright", na.label = "No Cases")


```


Africa {data-orientation=rows data-icon="fa-globe-africa"}
=====================================

Row
-----------------------------------------------------------------------

### Total {.value-box}

```{r}

flexdashboard::valueBox(value = paste(format(sum(AFR$Cnf, na.rm = T), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```

### Active {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(AFR$Active, na.rm = T), big.mark = ","), "", sep = " "),
         caption = "Active", icon = "fas fa-gratipay", 
         color = active_color)

```


### Recovered {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(AFR$Rec, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(AFR$Rec, na.rm = TRUE) / sum(AFR$Cnf), 1), 
                       "%)", sep = ""), 
         caption = "Recovered", icon = "fas fa-heartbeat", 
         color = recovered_color)

```

### Deaths {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(AFR$Dth, na.rm = TRUE), 
                                             big.mark = ","), " (",
                       round(100 * sum(AFR$Dth, na.rm = TRUE) / sum(AFR$Cnf), 1), 
                       "%)", sep = ""),
         caption = "Deaths", icon = "fas fa-angellist", 
         color = death_color)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### African Region

```{r}
#add africa countries boundaries
africa_countries <- readOGR(paste0("Africa/africa_countries.shp"), verbose = FALSE)
colnames(africa_countries@data) <- c("Country", "Long", "Lat")

africa_countries@data <-africa_countries@data %>%
  mutate(Country = as.character(Country),
         Country =  ifelse(Country=="Cape Verde","Cabo Verde",
                          ifelse(Country=="RÃfÂ©union","Reunion" ,
                                 ifelse(Country=="Eswatini\r\nEswatini\r\nEswatini","Eswatini" ,
                                 ifelse(Country=="Mayotte","Mayotte",Country)))))


AFR$Country <- as.character(AFR$Country)


d <- merge(africa_countries, AFR, by.x = "Country", by.y = "Country", duplicateGeoms = T, sort=FALSE, all.x = F)

d@data <-d@data %>% 
  dplyr::filter(AfricaCheck!=0)


bins <- c(0,1000,10000,20000,30000,40000,50000, Inf)
pal <- colorBin("YlOrRd", domain = d@data$Active, bins = bins)
#labels <- paste("Total Confirmed: ", d@data$Country.Region, d@data$TotalCases, paste0("People"))
labels <- sprintf(paste0("<strong>%s</strong><br/>",
        "Active: ",
        #d@data$Active,
        purrr::map(glue::glue("<span style='color: {active_color};'> {d@data$Active}</span>"),htmltools::HTML),
        
        "<br>",
        "Recovered: ",
        #d@data$Rec,
        purrr::map(glue::glue("<span style='color: {recovered_color};'> {d@data$Rec}</span>"),htmltools::HTML),
        "<br>",
        "Deaths: ",
        #d@data$Dth,
        purrr::map(glue::glue("<span style='color: {death_color};'> {d@data$Dth}</span>"),htmltools::HTML),
        "<br>"
      ),
                  d@data$Country, d@data$Active) %>%
  lapply(htmltools::HTML)

  africa_map <-leaflet() %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>% 
  addPolygons(data = d, 
              fillColor = ~pal(d@data$Active), 
              weight = 2, opacity = 1,
              color = "black", dashArray = "3", 
              fillOpacity = 0.7,
              highlight = highlightOptions(weight = 2.5, 
                                           color = "#0000f7",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = TRUE),
              label = labels, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px", direction = "auto"))  
 africa_map %>%  addLegend(pal = pal, values = d@data$Active, opacity = 0.7,
                             title = glue::glue("{sum(AFR$AfricaCheck, na.rm=T)} Countries Cases:<br>(Total Active: {paste('',format(sum(d@data$Active, na.rm=T), big.mark = ','), sep =' ')})"),
                             position = "bottomright", na.label = "No Cases")
```


### Africa Smooth Trend 

```{r}
smoothtrend <- Main.df %>% filter(AfricaCheck==1) %>% 
  mutate(Active = Confirmed - (Recovered+Deaths)) %>% 
  group_by(Dates,Country) %>% 
  summarise(Confirmed = max(Confirmed, na.rm = T),
            Active = max(Active, na.rm = T),
            Recovered = max(Recovered, na.rm = T),
            Deaths = max(Deaths, na.rm = T)) %>% 
  group_by(Dates) %>% 
  summarise(Confirmed = sum(Confirmed, na.rm = T),
            Active = sum(Active, na.rm = T),
            Recovered = sum(Recovered, na.rm = T),
            Deaths = sum(Deaths, na.rm = T)) %>% 
  
  tidyr::gather(Categories, TotalCases,Confirmed: Deaths)

cols<- c("purple","#1197fb","#ff6601","forestgreen")
hc <- hchart(smoothtrend, type = "line", hcaes(x = Dates, y = TotalCases, group = Categories)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Africa Daily Trend", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Africa Trends") %>% 
  hc_subtitle(text = paste(format(max(smoothtrend$TotalCases, na.rm = T),big.mark = ","),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_darkunica()) %>% 
  hc_colors(cols)

hc
```

Kenya {data-orientation=rows data-icon="fa-map-marker-alt"}
=====================================

```{r}
kenya<- Main.df %>% filter(Country=="Kenya") %>% 
  mutate(Active = (Confirmed - (Deaths + Recovered)))
  
tmonths <- kenya %>% 
  group_by(Country, Year_Month) %>% 
  summarise(Confirmed = max(Confirmed, na.rm = T),
            Deaths = max(Deaths, na.rm = T),
            Recovered = max(Recovered, na.rm = T)) %>% 
  group_by(Year_Month) %>% 
  #ungroup() %>% 
  summarise(Confirmed = sum(Confirmed, na.rm = T),
            Deaths = sum(Deaths, na.rm = T),
            Recovered = sum(Recovered, na.rm = T)) %>% 
  tidyr::gather(Categories, TotalCases, Confirmed:Recovered)
```

Row
-----------------------------------------------------------------------

### Total {.value-box}

```{r}

flexdashboard::valueBox(value = paste(format(max(kenya$Confirmed, na.rm = T), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```

### Active {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(max(kenya$Active, na.rm = T), big.mark = ","), "", sep = " "),
         caption = "Active", icon = "fas fa-gratipay", 
         color = active_color)

```


### Recovered {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(max(kenya$Recovered, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * max(kenya$Recovered, na.rm = TRUE) / max(kenya$Confirmed), 1), 
                       "%)", sep = ""), 
         caption = "Recovered", icon = "fas fa-heartbeat", 
         color = recovered_color)

```

### Deaths {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(max(kenya$Deaths, na.rm = TRUE), 
                                             big.mark = ","), " (",
                       round(100 * max(kenya$Deaths, na.rm = TRUE) / max(kenya$Confirmed), 1), 
                       "%)", sep = ""),
         caption = "Deaths", icon = "fas fa-angellist", 
         color = death_color)
```


Column{.tabset}
-----------------------------------------------------------------------

 

```{r, eval=FALSE}
### Totals
Tt <- max(tmonths$TotalCases, na.rm = T)

hc <- hchart(tmonths, type = "column", hcaes(x = Year_Month, y = TotalCases)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Kenya Cumulative Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Kenya Cumulative Total Number of Cases") %>% 
  hc_subtitle(text = paste(Tt,"Cases", sep = " ")) %>% 
   hc_add_theme(hc_theme_monokai())

hc

```


### Total  Individual  Months

```{r}

xxx<- Main.df %>% filter(Country=="Kenya") %>% 
  
  mutate(NewConfirmed = Confirmed - lag(Confirmed, default = first(Confirmed)),
         NewRecoveries = Recovered - lag(Recovered, default = first(Recovered)),
         NewDeaths = Deaths - lag(Deaths, default = first(Deaths)),
         NewActive = NewConfirmed -(NewDeaths+NewRecoveries)) %>% 
  group_by(Year_Month) %>% 
  summarise(TotalConfirmed = sum(NewConfirmed, na.rm = T),
            TotalRecovery = sum(NewRecoveries, na.rm = T),
            TotalDeaths = sum(NewDeaths, na.rm = T),
            TotalActive = sum(NewActive, na.rm = T)) %>% 
  pivot_longer(TotalConfirmed:TotalActive, names_to = "Category", values_to = "TotalCases") %>% 
  mutate(Category= as.factor(Category),
         Category = factor(Category, 
                           levels = c("TotalConfirmed","TotalActive","TotalRecovery","TotalDeaths"),
                           labels = c("TotalConfirmed","TotalActive","TotalRecovery","TotalDeaths")))
custom_colours<- viridis(4) 
custom_colours<-c("#f92672","#65d6ec","#a6e22e","#ff6601")
custom_colours<-c("#800080","#1197fb","#228b22","#ff6601")

Tt <- format(xxx %>% filter(Category=="TotalConfirmed") %>% select(TotalCases) %>% sum, big.mark = ",")

hc <- hchart(xxx, 
             type = "column", 
             hcaes(x = Year_Month, y = TotalCases, group = Category),
             color = custom_colours ) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Kenya Monthly Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Kenya Monthly Total Number of Cases") %>% 
  hc_subtitle(text = paste(Tt,"Cases", sep = " ")) %>% 
   hc_add_theme(hc_theme_monokai())

hc
```


### Categorized Cases

```{r}
Tt2 <- max(tmonths$TotalCases, na.rm = T)
custom_colours<-c("#800080","#1197fb","#228b22","#ff6601")

hc <- hchart(tmonths, 
             type = "column", 
             hcaes(x = Year_Month, y = TotalCases, group = Categories)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Kenya Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Kenya Time Comparison of Coronavirus") %>% 
  hc_subtitle(text = paste(Tt2,"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_monokai())

hc

```




### Daily Trend 

```{r}
plotly::plot_ly(data = kenya, 
                x = ~ Dates, 
                y = ~ Active, 
                type = "bar", 
                name = "Active",
                marker = list(color = active_color)) %>%
  plotly::add_trace(y = ~ Recovered, 
                    name = "Recovered",
                    marker = list(color = recovered_color)) %>%
  plotly::add_trace(y = ~ Deaths, 
                    name = "Died",
                    marker = list(color = death_color)) %>%
  plotly::layout(barmode = 'stack',
                 
                 yaxis = list(title = "Total Cases",
                              type = "log"),
                 xaxis = list(title = "",
                              range = as.character(sort(unique(as.numeric(kenya$Active)),decreasing = FALSE))),
                 hovermode = "compare", 
                 margin =  list(b = 10, 
                                t = 10, 
                                pad = 2
                 ))
```

### Kenya Smooth Trend 

```{r}
smoothtrend <- kenya %>% select(Dates, Confirmed, Active, Recovered, Deaths) %>% 
  tidyr::gather(Categories, TotalCases,Confirmed: Deaths)

cols<- c("purple","#1197fb","#ff6601","forestgreen")
hc <- hchart(smoothtrend, type = "line", hcaes(x = Dates, y = TotalCases, group = Categories)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Kenya Daily Trend", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Kenyan Trends") %>% 
  hc_subtitle(text = paste(format(max(smoothtrend$TotalCases, na.rm = T),big.mark = ","),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_darkunica()) %>% 
  hc_colors(cols)

hc
```


### Predict Daily new cases 

```{r, results='asis'}
suppressWarnings({
source("C:\\Users\\Cyrus Muriithi\\Documents\\GithubRepos\\C19-trend\\Covid-Prediction Model.R")
})
dyplot.prophet(m, forecast)
```



Comparitive Trend {data-icon="fa-globe"}
=======================================================================

As COVID-19 continues its silent and sometimes deadly march across the world, what can be learned from those uncertain, early days when it first made an appearance at a food market in Wuhan, China? People, understandably, have questions.

Because countries have taken radically different approaches to testing, and have sometimes changed testing strategies from one week to the next, scientists have struggled to compare case rates between countries.

Another difficulty has been working out the proportion of people who die after becoming infected, because many cases are never confirmed. 

Travel restrictions, social distancing and lockdowns across Britain and elsewhere are all intended to suppress transmission of coronavirus.

For interactive Comparative trend, kindly visit:

<h2> [Trend Analysis](https://cyrusmuriithi.shinyapps.io/CoronaAfrica/)</h2>

```{r}

```



Credit {data-icon="fa-award"}
=======================================================================
```{r}
Startdate <- min(Main.df$Dates)
LatestDates <- max(Main.df$Dates)
```


**Datasource **

The Dashboard  contains data from the number of Coronavirus confirmed cases, deaths, and recovered cases for every country and every day:

  + _Start:_ `r Startdate`
  + _Latest Updated:_   `r LatestDates`

+ The data is provided by https://github.com/CSSEGISandData/COVID-19 and 
  - transformed to JSON by https://pomber.github.io/covid19/timeseries.json
  - [Pomber](https://github.com/pomber)

 
**Credits**

+ Recognition:

   - Data provided by JHU CSSE
   - COVID-19 data transformed to JSON by Pomber
   - Design layout motivated by a Sr Colleague: [johnmutua](http://covid19.locus-geosystems.com/)


**Packages**

* Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package. 
* Visualization - the [plotly](https://plot.ly/r/) package for the plots, [leaflet](https://rstudio.github.io/leaflet/) for the map and [highchart](http://jkunst.com/highcharter/) for interactive statistics

* Data manipulation - [tidyverse](https://www.tidyverse.org/)


**Note**

+ __All the data displayed in the site are gathered from these sources,  might sometime show outdated data and will take some time to sync__

+ __( Data Updated regularly updated using GitHub Actions. Every 3.AM EAT, Kenyan Time)__


**CONTACT:** 

*CYRUS HERDER*

+ <a href="mailto:C.Muriithi@cgiar.org?body=Please send me a copy of your new program!">Send Email</a>


