---
title: "Corona Africa"
# author: "Cyrus Herder"
# date: "3/24/2020"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    #source: embed
    theme: flatly
    orientation: rows
---


```{r setup, include=FALSE}
rm(list = ls())
library(flexdashboard)
library(shiny)
library(shinydashboard)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(shiny)
library(countrycode)
library(rvest)
library(xml2)
library(dplyr)
library(leaflet)
library(leafpop)
library(purrr)
library(tibble)
library(rgdal)
#setwd(normalizePath(dirname(rstudioapi::getActiveDocumentContext()$path)))
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
source("Cleaning.R")
```

Home {data-icon="fa-home"}
=====================================


Row
-----------------------------------------------------------------------


### Total {.value-box}

```{r}

flexdashboard::valueBox(value = paste(format(sum(Africa$Cnf, na.rm = T), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```

### Active {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(Africa$Active, na.rm = T), big.mark = ","), "", sep = " "),
         caption = "Active", icon = "fas fa-gratipay", 
         color = active_color)

```



### Recovered {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(Africa$Rec, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(Africa$Rec, na.rm = TRUE) / sum(Africa$Cnf), 1), 
                       "%)", sep = ""), 
         caption = "Recovered", icon = "fas fa-heartbeat", 
         color = recovered_color)

```

### Deaths {.value-box}

```{r}

flexdashboard::valueBox(value = paste(format(sum(Africa$Dth, na.rm = TRUE), 
                                             big.mark = ","), " (",
                       round(100 * sum(Africa$Dth, na.rm = TRUE) / sum(Africa$Cnf), 1), 
                       "%)", sep = ""),
         caption = "Deaths", icon = "fas fa-angellist", 
         color = death_color)
```




Row {.tabset .tabset-fade}
-----------------------------------------------------------------------


### Africa Cases Distribution

```{r}
AFR <- as.data.frame(Africa %>% filter(AfricaCheck==1)) %>% arrange(desc(Active))

AFR$Country <- factor(AFR$Country, levels = unique(AFR$Country)[order(AFR$Active, decreasing = TRUE)])
```

```{r df_summary}
plotly::plot_ly(data = AFR, 
                x = ~ Country, 
                y = ~ Active, 
                type = "bar", 
                name = "Active",
                marker = list(color = active_color)) %>%
  plotly::add_trace(y = ~ Rec, 
                    name = "Recovered",
                    marker = list(color = recovered_color)) %>%
  plotly::add_trace(y = ~ Dth, 
                    name = "Died",
                    marker = list(color = death_color)) %>%
  plotly::layout(barmode = 'stack',
                 
                 yaxis = list(title = "Total Cases",
                              type = "log"),
                 xaxis = list(title = "",
                              range = as.character(sort(unique(as.numeric(AFR$Active)),decreasing = FALSE))),
                 hovermode = "compare", 
                 margin =  list(b = 10, 
                                t = 10, 
                                pad = 2
                 ))

```




Global Cases Summary {data-orientation=columns data-icon="fa-globe"}
=====================================


Column
-----------------------------------------------------------------------

### Total Cases

```{r}
  
Tt <- max(Totals$TotalCases, na.rm = T)

hc <- hchart(Totals, type = "column", hcaes(x = Year_Month, y = TotalCases)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Total Number of Cases") %>% 
  hc_subtitle(text = paste(Tt,"Cases", sep = " ")) %>% 
   hc_add_theme(hc_theme_monokai())

hc

```

Column
-----------------------------------------------------------------------

### Total Cases
```{r}
Tt2 <- max(Totals$TotalCases, na.rm = T)

hc <- hchart(Totals, type = "column", hcaes(x = Year_Month, y = TotalCases, group = Categories)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "Time Comparison of Coronavirus") %>% 
  hc_subtitle(text = paste(Tt2,"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_monokai())

hc

```




January - Trends {data-navmenu="Global - Trends" data-icon="fa-signal"}
=======================================================================

Row{.tabset}
-----------------------------------------------------------------------

### Confirmed {data-navmenu="January"}
```{r}
Jan <- Overall %>% 
  filter(Month==1) %>% 
  tidyr::gather(Variables, Values, Confirmed:Recovered) %>% 
  group_by(Variables,Dates) %>% 
  summarise(Totals = round(sum(Values, na.rm = T),0)) %>% 
  filter(Variables=="Confirmed")

hc <- hchart(Jan, type = "line", hcaes(x = Dates, y = Totals, group = Variables)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "January 2020 Trends") %>% 
  hc_subtitle(text = paste(sum(Jan$Totals, na.rm = T),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_monokai())

hc
```

### Death vs Recovery {data-navmenu="January"}
```{r}
Jan <- Overall %>% 
  filter(Month==1) %>% 
  tidyr::gather(Variables, Values, Confirmed:Recovered) %>% 
  group_by(Variables,Dates) %>% 
  summarise(Totals = round(sum(Values, na.rm = T),0)) %>% 
  filter(Variables!="Confirmed")

hc <- hchart(Jan, type = "line", hcaes(x = Dates, y = Totals, group = Variables)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "January 2020 Trends") %>% 
  hc_subtitle(text = paste(sum(Jan$Totals, na.rm = T),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_darkunica())

hc
```


February - Trends {data-navmenu="Global - Trends" data-icon="fa-signal"}
=======================================================================

Row{.tabset}
-----------------------------------------------------------------------


### Confirmed {data-navmenu="February"}
```{r}
Jan <- Overall %>% 
  filter(Month==2) %>% 
  tidyr::gather(Variables, Values, Confirmed:Recovered) %>% 
  group_by(Variables,Dates) %>% 
  summarise(Totals = round(sum(Values, na.rm = T),0)) %>% 
  filter(Variables=="Confirmed")

hc <- hchart(Jan, type = "line", hcaes(x = Dates, y = Totals, group = Variables)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "February 2020 Trends") %>% 
  hc_subtitle(text = paste(sum(Jan$Totals, na.rm = T),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_monokai())

hc
```

### Death vs Recovery {data-navmenu="February"}
```{r}
Jan <- Overall %>% 
  filter(Month==2) %>% 
  tidyr::gather(Variables, Values, Confirmed:Recovered) %>% 
  group_by(Variables,Dates) %>% 
  summarise(Totals = round(sum(Values, na.rm = T),0)) %>% 
  filter(Variables!="Confirmed")

hc <- hchart(Jan, type = "line", hcaes(x = Dates, y = Totals, group = Variables)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "February 2020 Trends") %>% 
  hc_subtitle(text = paste(sum(Jan$Totals, na.rm = T),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_darkunica())

hc
```

March - Trends {data-navmenu="Global - Trends" data-icon="fa-signal"}
=======================================================================

Row{.tabset}
-----------------------------------------------------------------------


### Confirmed {data-navmenu="March"}
```{r}
Jan <- Overall %>% 
  filter(Month==3) %>% 
  tidyr::gather(Variables, Values, Confirmed:Recovered) %>% 
  group_by(Variables,Dates) %>% 
  summarise(Totals = round(sum(Values, na.rm = T),0)) %>% 
  filter(Variables=="Confirmed")

hc <- hchart(Jan, type = "line", hcaes(x = Dates, y = Totals, group = Variables)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "March 2020 Trends") %>% 
  hc_subtitle(text = paste(sum(Jan$Totals, na.rm = T),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_monokai())

hc
```

### Death vs Recovery {data-navmenu="March"}
```{r}
Jan <- Overall %>% 
  filter(Month==3) %>% 
  tidyr::gather(Variables, Values, Confirmed:Recovered) %>% 
  group_by(Variables,Dates) %>% 
  summarise(Totals = round(sum(Values, na.rm = T),0)) %>% 
  filter(Variables!="Confirmed")

hc <- hchart(Jan, type = "line", hcaes(x = Dates, y = Totals, group = Variables)) %>% 
  hc_xAxis(title = list(text = "Months")) %>% 
  hc_yAxis(title = list(text = "Number of Cases")) %>% 
  hc_chart(type = "Number of Cases", options3d = list(enabled = TRUE, beta = 0, alpha = 0)) %>% 
  hc_title(text = "March 2020 Trends") %>% 
  hc_subtitle(text = paste(sum(Jan$Totals, na.rm = T),"Cases", sep = " ")) %>% 
  hc_add_theme(hc_theme_darkunica())

hc
```

Africa {data-orientation=rows data-icon="fa-globe-africa"}
=====================================

Row
-----------------------------------------------------------------------

### Total {.value-box}

```{r}

flexdashboard::valueBox(value = paste(format(sum(AFR$Cnf, na.rm = T), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```

### Active {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(AFR$Active, na.rm = T), big.mark = ","), "", sep = " "),
         caption = "Active", icon = "fas fa-gratipay", 
         color = active_color)

```



### Recovered {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(AFR$Rec, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(AFR$Rec, na.rm = TRUE) / sum(AFR$Cnf), 1), 
                       "%)", sep = ""), 
         caption = "Recovered", icon = "fas fa-heartbeat", 
         color = recovered_color)

```

### Deaths {.value-box}

```{r}
flexdashboard::valueBox(value = paste(format(sum(AFR$Dth, na.rm = TRUE), 
                                             big.mark = ","), " (",
                       round(100 * sum(AFR$Dth, na.rm = TRUE) / sum(AFR$Cnf), 1), 
                       "%)", sep = ""),
         caption = "Deaths", icon = "fas fa-angellist", 
         color = death_color)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### African Region

```{r}
#add africa countries boundaries
africa_countries <- readOGR(paste0("Africa/africa_countries.shp"), verbose = FALSE)
colnames(africa_countries@data) <- c("Country", "Long", "Lat")

africa_countries@data <-africa_countries@data %>%
  mutate(Country = as.character(Country),
         Country =  ifelse(Country=="Cape Verde","Cabo Verde",
                          ifelse(Country=="RÃfÂ©union","Reunion" ,
                                 ifelse(Country=="Mayotte","Mayotte",Country))))


AFR$Country <- as.character(AFR$Country)


d <- merge(africa_countries, AFR, by.x = "Country", by.y = "Country", duplicateGeoms = T, sort=FALSE, all.x = F)

d@data <-d@data %>% 
  dplyr::filter(AfricaCheck!=0)


bins <- c(0, 10, 20, 50, 100, 200, 500,750, 1000, 1200, 1500, 2000, Inf)
pal <- colorBin("YlOrRd", domain = d@data$Active, bins = bins)
#labels <- paste("Total Confirmed: ", d@data$Country.Region, d@data$TotalCases, paste0("People"))
labels <- sprintf(paste0("<strong>%s</strong><br/>",
        "Active: ",
        #d@data$Active,
        purrr::map(glue::glue("<span style='color: {active_color};'> {d@data$Active}</span>"),htmltools::HTML),
        
        "<br>",
        "Recovered: ",
        #d@data$Rec,
        purrr::map(glue::glue("<span style='color: {recovered_color};'> {d@data$Rec}</span>"),htmltools::HTML),
        "<br>",
        "Deaths: ",
        #d@data$Dth,
        purrr::map(glue::glue("<span style='color: {death_color};'> {d@data$Dth}</span>"),htmltools::HTML),
        "<br>"
      ),
                  d@data$Country, d@data$Active) %>%
  lapply(htmltools::HTML)

  africa_map <-leaflet() %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>% 
  addPolygons(data = d, 
              fillColor = ~pal(d@data$Active), 
              weight = 2, opacity = 1,
              color = "black", dashArray = "3", 
              fillOpacity = 0.7,
              highlight = highlightOptions(weight = 5, 
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = TRUE),
              label = labels, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px", direction = "auto"))  
 africa_map %>%  addLegend(pal = pal, values = d@data$Active, opacity = 0.7,
                             title = glue::glue("Africa Cases:<br>(Total Active: {paste('',format(sum(d@data$Active, na.rm=T), big.mark = ','), sep =' ')})"),
                             position = "bottomright", na.label = "No Cases")

```

Credit {data-icon="fa-award"}
=======================================================================
```{r}
Startdate <- min(Main.df$Dates)
LatestDates <- max(Main.df$Dates)
```

**Datasource **

The Dashboard  contains data from the number of Coronavirus confirmed cases, deaths, and recovered cases for every country and every day:

  + _Start:_ `r Startdate`
  + _Latest Updated:_   `r LatestDates`

+ The data is provided by https://github.com/CSSEGISandData/COVID-19 and 
  - transformed to JSON by https://pomber.github.io/covid19.
  - [Pomber]("https://pomber.github.io/covid19/timeseries.json")

 
**Credits**

+ Recognition:

   - Data provided by JHU CSSE
   - COVID-19 data transformed to JSON by Pomber
   - Design layout motivated by a Sr Colleague: [johnmutua](http://covid19.locus-geosystems.com/)


  
**Packages**

* Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package. 
* Visualization - the [plotly](https://plot.ly/r/) package for the plots, [leaflet](https://rstudio.github.io/leaflet/) for the map and [highchart](http://jkunst.com/highcharter/) for interactive statistics

* Data manipulation - [tidyverse](https://www.tidyverse.org/)


**Note**

+ __All the data displayed in the site are gathered from these sources,  might sometime show outdated data and will take some time to sync__

+ __( Data Updated regularly updated using GitHub Actions.)__